---
title: "PSTAT 131"
author: "Qingyang Fu"
date: "2022-09-27"
output: html_document
---

```{r}
library(tidyverse)
library(tidymodels)
library(ISLR)
```


Q1
Supervised learning uses linear regression, logistic regression, k-nearest neighbors, decision trees, random forests, support vector machine, and neural networks.
Unsupervised learning uses principal component analysis, k-means clustering, hierarchical clustering, and neural networks.
Supervised learning take an actual data Y as supervisor, and unsupervised learning does not has an actual data value for Y. 


Q2
In machine learning, for regression model, Y is quantitative and it predicts numerical values. While for Classification model, Y is qualitative and predicts categorical values.


Q3
Regression: MSE & RMSE
Classification: Accuracy & Confusion Matrix


Q4
Descriptive Models: Choose model to best visually emphasize a trend in data
Predictive Models: To predict Y with minimum reducible error and is not focused on hypothesis test
Inferential Models: To test theroeis, possibly causal calims, and state relationship between outcome and predicator(s)


Q5
Mechanistic model is parametric, and it assumes a parametric form for f and won't match true unknown f. It can add parameters to be more flexible, but too many will cause over-fitting.
Empirically-driven is non-parametric, there will be no assumption about f, and it requires a larger number of observations. This is more flexible by default but can be over-fitting as well. 

I think that mechanistic model should be easier to understand, since it assume a parametric form for f and usually less flexible than empirically- driven model. Thus the model has better interpretability. 

Bias-Variance trade-off is that bias and variance has a negative relationship. Which means fora simple model, it has high bias but low variance, while for a flexible model, it has low bias but high variance.


Q6
Given a voter’s profile/data, how likely is it that they will vote in favor of the candidate?
  This is predictive model, since a voter's data is given and it is aimed to predict the result with minimum reducible error and is not focused on hypothesis test
How would a voter’s likelihood of support for the candidate change if they had personal contact with the candidate?
  This is inferential model, since it is aimed to test theories that if there is a relationship between the voter's support and their personal contact with the candidate.



Exercise 1:
We can tell from the diagram that most of the vehicles drive 25 to 30 miles per gallon, while least of the vehicles drive above 35 miles per gallon.
```{r}
data("mpg")
hist(mpg$hwy, main="Highway Miles per Gallon", breaks=5, xlim = range(10:45), xlab="hwy",ylab= "Frequency")
```

Exercise 2:
There is no obvious outliers, and as the hwy increases, cty increases as well, which show there is a possible positive linear relationship between hwy and cty.
```{r}
ggplot(mpg, aes(hwy, cty)) + 
  geom_point(size=2, alpha=0.4) +
  labs(x="hwy", y="cty")
```

Exercise 3:
```{r}

```

Exercise 4:
There is outliers exists when cyl = 4 and 8.There seems to be a possible negative linear relationship between hwy and cyl. When the value of cyl increases, the value of hwy decreases.
```{r}
boxplot(hwy ~ cyl, data = mpg)
```

Exercise 5:
mpg has a negative correlation with cyl, disp, hp, wt, and carb. And positive relationship with all other variables. The relationships are making sense since there is a clear relationship between mpg and other variables that is there is a positive relationship, the mpg increases as the other variables increase. And if there is a neggative relationship, the mpg decreases as the other variables increases.
```{r}
data("mpg")
install.packages("corrplot")
library(corrplot)
```
```{r}
M <- cor(mtcars)
corrplot(M, method = 'number', type = "lower")
```

