---
title: "PSTAT 131"
author: "Qingyang Fu"
date: "2022-09-27"
output: html_document
---

```{r}
library(tidyverse)
library(tidymodels)
library(ISLR)
```


Q1
Supervised learning uses linear regression, logistic regression, k-nearest neighbors, decision trees, random forests, support vector machine, and neural networks.
Unsupervised learning uses principal component analysis, k-means clustering, hierarchical clustering, and neural networks.
Supervised learning take an actual data Y as supervisor, and unsupervised learning does not has an actual data value for Y. 


Q2
In machine learning, for regression model, Y is quantitative and it predicts numerical values. While for Classification model, Y is qualitative and predicts categorical values.


Q3


Q4
Descriptive Models: Choose model to best visually emphasize a trend in data
Predictive Models: To predict Y with minimum reducible error and is not focused on hypothesis test
Inferential Models: To test theroeis, possibly causal calims, and state relationship between outcome and predicator(s)


Q5


Q6


Exercise 1:
```{r}



```

Exercise 2:
```{r}

```

Exercise 3:
```{r}

```

Exercise 4:
```{r}

```

Exercise 5:
```{r}

```
